Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-07-27 chap-incr-concl.tex
Add more sensible labels in a few places

% \pg{Plan for things that complete the original paper's story: add them by
%   revising that text and in that chapter.}
\chapter{Conclusion and future work}
\label{ch:incl-conclusion}
In databases, standard finite differencing technology allows incrementalizing
programs in a specific domain-specific first-order language of collection
operations.
Unlike other approaches, finite differencing transforms programs to programs,
which can in turn be transformed further.

>>>>

% \pg{Plan for things that complete the original paper's story: add them by
%   revising that text and in that chapter.}
\chapter{Conclusion and future work}
\label{ch:incr-conclusion}
In databases, standard finite differencing technology allows incrementalizing
programs in a specific domain-specific first-order language of collection
operations.
Unlike other approaches, finite differencing transforms programs to programs,
which can in turn be transformed further.
